Higher order unification for free!

### 2024-04-09 paper/main.tex
correction of a proof

\begin{proof}
  Trivial, since the unification is done between unification variables, which
  are by definition in \wellb.
\end{proof}

\begin{lemma}
  \Cref{prop:nf} holds, i.e., given a substitution $\sigma$ and a \linketa $l$,
  after the activation of $l$, $\wellb(\sigma)$ holds.
\end{lemma}

>>>>

\begin{proof}
  The unification is done between the \rhs of two
  \linketa. Both \rhs has the shape $\lambda x.t$, with $\wellb(t)$, therefore,
  the unification is done between well-behaved terms.
\end{proof}

\begin{lemma}
  The introduction of \linketa guarantees \fullref{prop:nf}
  \label{lemma:unif-wellb}
\end{lemma}
